---
title: "R Codes"
# date: '`r format(Sys.Date(), "%Y-%B-%d")`'
output:
  html_document:
    code_folding: hide
    number_sections: yes
    theme: united
    toc: yes
  html_notebook:
    code_folding: hide
    number_sections: yes
    theme: united
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r global_options, include=FALSE}
library(rmarkdown)
library(knitr)
options(encoding="utf-8")
options(scipen=1, digits=2)

```

# Load commonly used library, others are loaded in each chunk as needed.
* Don't put the library loading code in chunk with option cache=TRUE, since it may not be executed.
* Check existence of working directory and create them if don't exist
```{r loading common libs, message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
library(readr)
library(readxl)
library(fixest)

pdd <- getwd()

print(paste("The root folder is",getwd()))

```


# Prepare LinkedIn link/url file
* Use Python code to download
```{r eval=FALSE, include=FALSE}
l_list <- readxl::read_xlsx(file.path(pdd,"input/Virginia CPA Database 10_28_2024.xlsx"),sheet = "List") %>% 
  rename_with(~str_remove_all(.,"\\s+"),everything()) %>% 
  rename_with(str_to_lower) %>% 
  ungroup()

l_list_done <- list.files(file.path(pdd,"linkedInprofiles")) %>% as_tibble() %>% 
  mutate(value=str_remove_all(value,".*_")) %>% 
  mutate(value=str_remove_all(value,".html")) %>% 
  distinct() %>% 
  rename(license_no=value) %>% 
  mutate(license_no=as.integer(license_no)) %>% 
  ungroup()

linkedIn="https://www.linkedin.com/in/"
dd_a1 <- l_list %>% 
  select(license_no,linkedinwebsite) %>% 
  mutate(linkedinwebsite=str_remove_all(linkedinwebsite,linkedIn)) %>% 
  separate(linkedinwebsite,into = c("username",NA),sep = "/|\\?") %>% 
  drop_na() %>% 
  ungroup()
  
dd_a2 <- dd_a1 %>% 
  mutate(linkedinwebsite=paste0(linkedIn,username)) %>% 
  anti_join(l_list_done) %>% 
  ungroup()

dd_a2 %>% write_csv(file.path(pdd,"urls_clean_to_be_done.csv"))

```

## Parse out call data from transcript pages.
* Assume call transcripts are downloaded from stops above and saved to local drive as html files.
```{r message=FALSE, warning=FALSE}
library(rvest)
library(xml2)
ddir <- file.path(pdd,"linkedInprofiles")
kk_files <- list.files(path =ddir, pattern=".+html$",recursive=FALSE,all.files=FALSE,full.names=TRUE) %>%
  as_tibble() %>% 
  ungroup()

ct<<-0
page_content <- kk_files %>% 
  # slice_head(n = 5) %>% # Parse the first 5 files. Comment this line to parse all the files.
  mutate(rs=map(value, function(x){
    ct<<-ct+1
    print(paste("Parsing page",ct,":",x))
    
    dd_i1=read_html(x) #%>% html_element(".tailwind-article-body") 
    
    # Parse information from each row
    # only find the p and h2 direct decedents
    dd_fullname <- dd_i1 %>% html_elements("a>h1[class*='RIbnCAsTbWzbdDScQkPGXRrQHSaITKZWQhh']") %>% html_text2()
    dd_curtitle <- dd_i1 %>% html_elements("div[class='text-body-medium break-words']") %>% html_text2()
    dd_curremployer <- dd_i1 %>% html_elements("ul[class='hNDqkOikRDuBnmMRQBsDppnmDpFtRoVtlI']>li:first-child") %>% html_text2()
    dd_currschool <- dd_i1 %>% html_elements("ul[class='hNDqkOikRDuBnmMRQBsDppnmDpFtRoVtlI']>li:last-child") %>% html_text2()
    dd_location <- dd_i1 %>% html_elements("div>span[class='text-body-small inline t-black--light break-words']") %>% html_text2()
    dd_followers <- dd_i1 %>% html_elements("ul[class='MWaduJUIKMfhoQkrCRhYTGnTIpgfQk dZtxzUycPMMyfWWwoWSxLMWZifggjaCUWyn']>li[class='text-body-small t-black--light inline-block']") %>% html_text2()
    dd_connections <- dd_i1 %>% html_elements("ul[class='MWaduJUIKMfhoQkrCRhYTGnTIpgfQk dZtxzUycPMMyfWWwoWSxLMWZifggjaCUWyn']>li[class='text-body-small']") %>% html_text2()
    dd_about <- dd_i1 %>% html_elements("section>div[class='display-flex ph5 pv3'] span[class='visually-hidden']") %>% html_text2()
    # dd_section_exp <- dd_i1 %>% html_elements("section:has(>div[id='experience'])") 
    # dd_section_exp <- dd_i1 %>% html_elements(xpath = "//section[div[@id='experience'") 
    dd_section_exp_list <- dd_i1 %>% html_elements("#experience + div+div>ul[class^='EFLaOlCrViAfIXmeNoOeVWbBsMuTBSwkXZDPU']>li")
    dd_section_exp <- dd_section_exp_list %>% map_df(function(y) {
      # y=dd_section_exp_list[1]
      y0=y %>% html_elements("div:nth_child(2)>div>div[class*='display-flex flex-column full-width']")
      f_title=y0 %>% html_elements("div span[class='visually-hidden']") %>% html_text2()
      f_company_n_type=y0 %>% html_elements("span[class='t-14 t-normal'] span[class='visually-hidden']") %>% html_text2()
      f_year_duration_location=y0 %>% html_elements("span[class$='t-black--light'] span[class='visually-hidden']") %>% html_text2() 
      
      tibble(f_title,f_company_n_type,f_year_duration_location)
      
    })
    
    dd_section_edu_list <- dd_i1 %>% html_elements("#education + div+div>ul[class^='EFLaOlCrViAfIXmeNoOeVWbBsMuTBSwkXZDPU']>li")
    dd_section_edu <- dd_section_edu_list %>% map_df(function(y) {
      # y=dd_section_edu_list[1]
      y0=y %>% html_elements("div:nth_child(2)>div[class*='display-flex flex-row justify-space-between']")
      f_school=y0 %>% html_elements("div[class='display-flex flex-wrap align-items-center full-height'] span[class='visually-hidden']") %>% html_text2()
      f_degree=y0 %>% html_elements("span[class='t-14 t-normal'] span[class='visually-hidden']") %>% html_text2()
      f_year_duration=y0 %>% html_elements("span[class$='t-black--light'] span[class='visually-hidden']") %>% html_text2()
      
      tibble(f_school,f_degree,f_year_duration)
    })
    
    
    dd_t1 <- tibble(fullname=ifelse(length(dd_fullname)>0,dd_fullname,NA),
                    curtitle=ifelse(length(dd_curtitle)>0,dd_curtitle,NA),
                    curremployer=ifelse(length(dd_curremployer)>0,dd_curremployer,NA),
                    currschool=ifelse(length(dd_currschool)>0,dd_currschool,NA),
                    location=ifelse(length(dd_location)>0,dd_location,NA),
                    followers=ifelse(length(dd_followers)>0,dd_followers,NA),
                    connections=ifelse(length(dd_connections)>0,dd_connections,NA),
                    experiences=list(dd_section_exp),
                    educations=list(dd_section_edu),
                    about=ifelse(length(dd_about)>0,dd_about,NA)) %>% 
      mutate(across(where(is.character),str_squish))
  }
  ))


page_content_raw <- page_content %>% unnest(rs) %>% 
  rename(value=value) %>% 
  mutate(value=str_remove_all(value,".*/")) %>% 
  separate(value,into = c(NA,NA,"rowid","license"),sep = "_") %>% 
  mutate(rowid=as.integer(rowid)) %>% 
  mutate(license=str_remove(license,".html")) %>% 
  arrange(rowid) %>% 
  ungroup()

page_content_raw %>% write_rds(file.path(pdd,"output/CAP_data_raw.rds"))
print("A sample of raw page content are shown below.")
page_content_raw

```

# Part 3: Clean and organize the data
```{r message=FALSE, warning=FALSE}
dd_a1  <- read_rds(file.path(pdd,"CAP_data_raw.rds"))

dd_basics <- dd_a1 %>% select(-c(experiences,educations)) %>% 
  mutate(across(where(is.character),str_squish)) %>% 
  ungroup()

# dd_basics %>% clipr::write_clip()

dd_b1 <- dd_a1 %>% select(rowid,license,fullname,experiences) %>% unnest(experiences) 
dd_exp <- dd_b1 %>% 
  group_by(rowid,license,fullname,f_title,f_company_n_type) %>% 
  summarise(f_year_duration_location=paste(f_year_duration_location,collapse = "|")) %>% 
  separate(f_company_n_type,into = c("company","type"),sep = "\\·") %>% 
  separate(f_year_duration_location,into = c("yd","location"),sep = "\\|") %>% 
  separate(yd,into = c("year_range","duration"),sep = "\\·") %>% 
  mutate(across(where(is.character),str_squish)) %>% 
  ungroup()
# dd_exp %>% clipr::write_clip()

dd_c1 <- dd_a1 %>% select(rowid,license,fullname,educations) %>% unnest(educations) 
dd_edu <- dd_c1 %>% 
  separate(f_year_duration,into = c("ystart","yend"),sep = "\\-") %>% 
  mutate(across(where(is.character),str_squish)) %>% 
  ungroup()
# dd_edu %>% clipr::write_clip()

```


# Part 4: Calculate additional metrics such as total years of experices and educations.
* Create variable professional experience
```{r message=FALSE, warning=FALSE}
# to be added.

```

